%!TEX TS-program = xelatex
\documentclass[a4paper]{article}

\usepackage[dvipsnames]{xcolor}
\usepackage[most]{tcolorbox}
\usepackage{eso-pic}
\usepackage{fontawesome5}
\usepackage{fontspec}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{titlesec}
\usepackage{titling}

\setmainfont{Libertinus}[
    Path=./fonts/Libertinus/,
    Extension=.otf,
    UprightFont=*Serif-Regular,
    BoldFont=*Serif-Bold,
    ItalicFont=*Serif-Italic,
    BoldItalicFont=*Serif-BoldItalic,
]

\setsansfont{Junction}[
    Path=./fonts/junction/,
    Extension=.otf,
    UprightFont=*-regular,
    BoldFont=*-bold,
    ItalicFont=*-light,
]

\hypersetup{
    colorlinks=true,
    urlcolor=MidnightBlue,
}

\newgeometry{top=0.5cm}
\setlength{\parindent}{0pt}
\pagenumbering{gobble}

\renewcommand{\familydefault}{\rmdefault}

\definecolor{bestgray}{RGB}{16,16,16}%

\newtcolorbox{widebox}[1][]{spread sidewards, left*=4cm, right*=0pt, colback=bestgray!10, coltext=white!100, colframe=bestgray!100, colback=bestgray!100, enhanced, sharp corners, halign=right}

\renewcommand{\maketitle}{
  \begin{widebox}
    {\huge\bfseries\textsf\theauthor} \\
    \medskip{}
    \begin{tabular}{@{}c|c@{}}
        \faIcon{linkedin} \textsf{\applinkedinurl{}} & \faIcon{github} \textsf{\appgithuburl{}}
    \end{tabular}
    \begin{tabular}{@{}c|c@{}}
        \faIcon{mobile} \textsf{\appcellphone{}} & \faIcon{envelope} \textsf{\appemail{}}
    \end{tabular} \\
    \medskip{}
    \faIcon{home} \textsf{\appaddresslineone{}} \\
    \textsf{\appaddresslinetwo{}} \\
    \textsf{\appaddresslinethree{}}
  \end{widebox}
}
\titleformat{\section}{\huge\bfseries\center}{}{0em}{\textsf}[\titlerule]
\titleformat{\subsection}{\bfseries\Large}{}{0em}{\textsf}
\titleformat{\subsubsection}[runin]{\bfseries}{}{0em}{\textsf}

\begin{document}

\author{\textsf{\appfirstname{} \applastname{}}}

\maketitle

\section{Professional Experience}
\begin{minipage}{\textwidth}
\textbf{System Administrator}\par
\textit{Nashville Music City Center -- Nashville, TN}\hfill Dec 2022 -- Present

\medskip
\textbf{Overview:} As a System Administrator, I oversee Microsoft Hyper-V and VMware ESXi clustered production environments, and manage various Cisco, Dell, and HP hardware and software. My responsibilities also include conducting cybersecurity audits and implementing network and server security patches.

\medskip
\textbf{Key Achievements:} 
\begin{itemize}
    \item Successfully deployed new infrastructure and optimized existing infrastructure, ensuring seamless production.
    \item Conducted regular team meetings to discuss projects and ensure system reliability.
    \item Effectively reduced network-wide vulnerabilities by proactively implementing security patches.
    \item Implemented a development environment for sandboxing, promoting software testing and innovation.
\end{itemize}
\end{minipage}

\vspace{10pt}
\begin{minipage}{\textwidth}
\textbf{Technology Support Technician}\par
\textit{PacSun -- Anaheim, CA}\hfill Nov 2021 -- Nov 2022

\medskip
\textbf{Overview:} I worked with stores in the United States and Puerto Rico to troubleshoot network, VOIP, POS/MPOS, and hardware/software issues. I also assisted with issues related to payment processing and order management, and resolved issues with Active Directory user configuration, as well as Cisco AnyConnect incorporation.

\medskip
\textbf{Key Achievements:}
\begin{itemize}
    \item Ensured all technological issues were resolved in a timely manner during Black Friday, Christmas, and New Year holidays.
    \item Developed team-wide network troubleshooting tools written in Python.
\end{itemize}
\end{minipage}

\vspace{10pt}
\begin{minipage}{\textwidth}
\textbf{Help Desk Technology Associate}\par
\textit{Hot Topic, Inc. -- City of Industry, CA}\hfill Aug 2021 -- Nov 2021

\medskip
\textbf{Overview:} I worked with stores in the United States, Canada, and Puerto Rico to troubleshoot network, POS/MPOS, and hardware/software issues. I also assisted with issues relating to payment processing and order management, and utilized Cisco Meraki to troubleshoot Cisco router hardware and firmware.

\medskip
\textbf{Key Achievements:}
\begin{itemize}
    \item Developed department-wide remote administration tools to increase the efficiency of the helpdesk team, guaranteeing optimum support.
\end{itemize}
\end{minipage}

\vspace{10pt}
\begin{minipage}{\textwidth}
\textbf{Technology Support Specialist}\par
\textit{GW Security, Inc. -- South El Monte, CA}\hfill Aug 2020 -- Jun 2021

\medskip
\textbf{Overview:} In my role as a Technology Support Specialist, I provided essential assistance in troubleshooting hardware, software, and network issues for NVRs, DVRs, and XVRs.

\medskip
\textbf{Key Achievements:}
\begin{itemize}
    \item Successfully upgraded the help desk infrastructure by implementing and testing a new ticketing system.
    \item Utilized the system's new features to ensure that the Service Level Agreement (SLA) was met and incidents were resolved quickly and efficiently.
\end{itemize}
\end{minipage}

\section{Technical Skills}
\begin{minipage}{\textwidth}
\begin{itemize}
    \apptechnicalskills{}
\end{itemize}
\end{minipage}

\section{Projects}
\subsection{Self-hosted High-Availability Kubernetes Cluster}
\begin{itemize}
    \item Designed and implemented a self-hosted Kubernetes cluster utilizing Talos Linux, Flux, and SOPS for streamlined and secure management.
    \item Employed best practices for security, including encrypted cluster secrets and a strong understanding of Kubernetes deployments and management.
    \item Automated continuous integration and delivery using GitHub Actions and linting techniques, ensuring reliable and efficient operations.
    \item GitHub repository: \url{https://github.com/Euvaz/GitOps-Home}
\end{itemize}

\subsection{Portfolio Website with Go, Python, and Microservices}
\begin{itemize}
    \item Implemented a portfolio website using Go's Gin library as the web framework and multitemplate library for efficient rendering.
    \item Integrated a Python script that utilizes GitHub's API to retrieve project repository data, which is stored in an SQLite database and propagated to the website's pages.
    \item Optimized for microservice deployment using Docker images and subjected to rigorous linting, testing, and building processes through GitHub Actions.
    \item Demonstrated web development skills and professional experience while providing advanced functionalities to keep visitors up-to-date on the latest endeavors.
    \item GitHub repository: \url{https://github.com/Euvaz/InfraFolio}
\end{itemize}

\subsection{LaTeX Resume Generator with Templating and Secure Macros}
\begin{itemize}
    \item Developed a highly customizable resume generator using LaTeX and Bash, featuring template-based generation and secure macros encrypted with SOPS\@.
    \item Automated the build and delivery process using multiple GitHub Actions for continuous integration and delivery, including linting, compilation, and delivery techniques.
    \item GitHub repository: \url{https://github.com/Euvaz/TexCV}
\end{itemize}

\section{Education}
\subsection{Degrees}
\begin{minipage}{\textwidth}
\textbf{AS Cybersecurity}\par
Rio Hondo College -- South El Monte, CA -- May-2021
\end{minipage}

\vspace{20pt}
\subsection{Certificates}
\begin{minipage}{\textwidth}
\textbf{Cloud Computing Practitioner}\par
Rio Hondo College -- South El Monte, CA -- May-2021

\medskip
\textbf{Cybersecurity}\par
Rio Hondo College -- South El Monte, CA -- May-2021

\medskip
\textbf{Ethical Hacker}\par
Rio Hondo College -- South El Monte, CA -- May-2021

\medskip
\textbf{Cybersecurity Technician}\par
Rio Hondo College -- South El Monte, CA -- May-2021
\end{minipage}

\end{document}
